Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-29 paper/paper.tex
update paper figures

\bigskip
The management generates a huge amount of data.
During the last few years, there was an explosion of the number of of works at
the interface of HPC and bigdata, dealing with learning algorithms
(including the authors of this paper~\cite{Gaussier2015ImprovingBB}).
Most of these studies target the process to determine more or less accurately
the value of some specific key parameters, with the idea of
learning better estimates should improve the performances of the resource
manager.

@@

\subsubsection{Traces}

@@

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[scale=0.6]{ctc_sp.pdf}
  \includegraphics[scale=0.6]{kth_sp.pdf}\\
  \includegraphics[scale=0.6]{sdsc_s.pdf}
  \includegraphics[scale=0.6]{sdsc_b.pdf}\\
  \includegraphics[scale=0.6]{anl_in.pdf}
  \includegraphics[scale=0.6]{unilug.pdf}

  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the FullFeedback, NoisyFeedback and EpsilonGreedy
    policies. The average is obtained by resampling the original trace 100
    times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling. Each figure is a different trace, and this
figure is followed-up in figure~\ref{fig:follow} for the CEA-Curie log.}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{cea_cu.pdf}

  \caption{Follow-up from figure~\ref{fig:small}, plot for the CEA-Curie log.}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{all.pdf}
  \caption{Share of the policies chosen by the Noisy policy. The average
  choice is obtained by resampling the original trace 100 times and
  aggregating by date.}
  \label{fig:all}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{mosaic_bandit.pdf}
  \caption{Share of the policies chosen by Epsilon-Greedy as a function of time.
  The average choice is obtained by resampling the original trace 100 times and
  aggregating by date.}
  \label{fig:mosb}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.6]{mosaic_noisy.pdf}
  \caption{Share of the policies chosen by the Noisy policy. The average
  choice is obtained by resampling the original trace 100 times and
  aggregating by date.}
  \label{fig:mosn}
\end{figure}

>>>>

\bigskip
The management generates a huge amount of data.
During the last few years, there was an explosion of the number of of works at
the interface of HPC and bigdata, dealing with learning algorithms
(including the authors of this paper~\cite{learningruntimes}).
Most of these studies target the process to determine more or less accurately
the value of some specific key parameters, with the idea of
learning better estimates should improve the performances of the resource
manager.

@@

\subsubsection{Traces}
\label{sub:traces}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[scale=0.6]{variability.pdf}
  \caption{Variability in the weekly average waiting time in the KTH-SP2 trace (pre-processing described in subsection~\ref{sub:traces}) for a few policies.}
  \label{fig:mosn}
\end{figure*}

@@

\begin{figure*}[h]
  \centering
  \includegraphics[scale=0.6]{full-CTC-SP2.pdf}
  \includegraphics[scale=0.6]{full-KTH-SP2.pdf}\\
  \includegraphics[scale=0.6]{full-CEA-Curi.pdf}
  \includegraphics[scale=0.6]{full-SDSC-BLU.pdf}\\
  \includegraphics[scale=0.6]{full-SDSC-SP2.pdf}
  \includegraphics[scale=0.6]{full-ANL-Intr.pdf}

  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the FullFeedback, NoisyFeedback and EpsilonGreedy
    policies. The average is obtained by resampling the original trace 100
    times. The dashed lines represent the 10th and 90th percentiles of the
  values across this resampling. Each figure is a different trace, and this
figure is followed-up in figure~\ref{fig:follow} for the UniLu-Gaia log.}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.6]{full-UniLu-Ga.pdf}

  \caption{Follow-up from figure~\ref{fig:small}, plot for the UniLu-Gaia log.}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{UniLu-Ga.pdf}

  \caption{Evolution of the average cumulative waiting time improvement
    compared to EASY-FCFS of the policies $P_i$ for $i = 1 \ldots 10$. The
    average is obtained by resampling the original trace 100 times. The dashed
    lines represent the 10th and 90th percentiles of the values across this
  resampling. Each figure is a different trace, and this figure is followed-up
in figure~\ref{fig:follow} for the UniLu-Gaia log.}

  \label{fig:all}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.6]{mosaicbandit-UniLu-Ga.pdf}
  \caption{Share of the policies chosen by Epsilon-Greedy as a function of time.
  The average choice is obtained by resampling the original trace 100 times and
  aggregating by date.}
  \label{fig:mosb}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.6]{mosaic-UniLu-Ga.pdf}
  \caption{Share of the policies chosen by the Noisy policy. The average
  choice is obtained by resampling the original trace 100 times and
  aggregating by date.}
  \label{fig:mosn}
\end{figure}
